---
title       : Presentation Sninyapp
subtitle    : Coursera Data Product course
author      : Romain PHILIPPE
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## The subject

The goal of this small app is to display informations about a baseball player according to their name.
The informations come from the ***Hitters*** dataset. We have the salary, the number of hits, the league name, the division names ...<br><br>
We also display a histogram which represents the salaries of the whole set of datas. A red line indicate the salary of the selectioned player, and a green line represents the median salary of the players, so we can compare the difference of salary of the player selected with the other ones.


--- .class #id 

## The input of the app

There is only one input in this app : the name of the player. To do that we load the ISLR package.
```{r}
library(ISLR)
playersNames<-row.names(Hitters)
head(substr(playersNames, 2, nchar(playersNames)),20)
```

Then, we compute two small commands to extract the name of the player by removing the first character (-). We can see the R script above.

--- .class #id 

## The output of the app

There are two main outputs of this app : <br>

1. A histogram plot
2. A table

The histogram represents the density of salaries for all the players. We display two lines : one for the median of the salary and the other one containing the current salary. <br>
A table display informations about the player like the number of hits, number of runs, the league name and the division name.


--- .class #id 


## Conclusion

In the slidify presentation, I use a ***selectInput*** as an input and two differents outputs : an histogram (plotOutput) and a table (dataTableOutput). 

```{r, echo=FALSE}
library(ISLR)
hist(Hitters$Salary, col = 'darkgray', border = 'white')
lines(c(Hitters[10,]$Salary, Hitters[10,]$Salary), c(0, 200),col="red",lwd=5)
lines(c(median(na.omit(Hitters)$Salary), median(na.omit(Hitters)$Salary)), c(0, 200),col="green",lwd=5)
```
